Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-17 paper/main.tex
Trim table

@@

\footnotesize
\begin{tabular}{lp{3.5cm}lllllllll} \toprule \textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\

>>>>

    Event counts for frame-based features are reported in units of a thousand.

@@

\small
\begin{tabular}{lp{3.7cm}lllllllll} \toprule \textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
